### 2020-01-27 ChapterImplementation/chapterImplementation.tex
Updated: Mention of message order in Aura Implementation

%TODO: Talk about messages arriving in and out of order. RakNet's ordered feature
%TODO: Talk about edge-cases of multiple types of messages being sent in on tick.

>>>>

It is important to note that message order for the state of auras is important. For example, an aura exists for an object hosted on server 0 and is being broadcast to server 1. The object moves away from the boundary and after multiple frames is outside of the boundary trigger. Server 0 sends update message to server 1, to update the position of the aura and finally sends a delete aura message to server 1, when the object exists the boundary trigger. However, if the messages are received in the wrong order and an update message is delivered after the delete message is received and the aura deleted on server 1, server 1 will interpret the update message as a new aura being created, leading to an aura that should not exist. This aura may never be deleted, as the sending object might never send an aura update in the future. In order to prevent this, the messages use the ordered message feature of RakNet, which ensure the messages are read on the receiving server in the same order they are sent from the sending server.

%TODO: Talk about edge-cases of multiple types of messages being sent in on tick.
